---
title: "RWorksheet_lastname#3b"
author: "Mike Anthony Taltal"
date: "2022-11-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Create a data frame using the table below.
a. Write the codes
```{r}
info <- data.frame(
  Respondents = c(1:20),
  Sex = c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2),
  Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1),
  Persons_at_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_at_School = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Types_of_Houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
)
info
```
b.Describe the data. Get the structure or the summary of the data. 
```{r}
summary(info)
```
c.Is the mean number of siblings attending is 5?
```{r}
Siblings_at_School = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
mean(Siblings_at_School)
```
d. Extract the 1st two rows and then all the 
columns using the subsetting functions.Write the codes and its output.
```{r}
newinfo <- subset(info[1:2, 1:6, drop = FALSE])
newinfo
```
e. Extract 3rd and 5th row with 2nd and 4th column. 
Write the codes and its result.
```{r}
thirdandfifth <- subset(info [3:5, 2:4, drop = FALSE])
thirdandfifth 
```
f.Select the variable types of houses then store the vector that 
results as types_houses.Write the codes.
```{r}
types_houses <-  info [c(6)]
types_houses
```
g. Select only all Males respondent that their father occupation was farmer.
the codes and its output.
```{r}
males <- subset(info[c(3,11),c(2,3)])
males
```



h. Select only all females respondent that have greater than or equal 
to 5 number of siblings attending school. Write the codes and its outputs.
```{r}
zegzog <- subset(info[c(1:20), c(2,5)])
girls <- zegzog[info$Siblings_at_School >= 5,]
girls
```
2. Write a R program to create an empty data frame. Using the following codes:\
```{r}
df = data.frame(Ints=integer(),
                Doubles=double(), Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)
print("Structure of the empty dataframe: ")
print(str(df))
```

a. Describe the results.
#the result shows that the data frame consists of 5 variables and it is empty. 

3. Interpret the graph.

#the graph shows the negative, positie, neutral sentiments of the 
#twitter users per day from july 14 to july 21 2020. 



