---
title: "RWorksheet_Taltal#6"
author: "Mike Anthony Taltal"
date: "2022-11-25"
output: pdf_document
---


#Use the dataset mpg
```{r}
library(ggplot2)
data(mpg)
as.data.frame(data(mpg))
str(mpg)
library(tinytex)
```
```{r, data1}
data("mpg")
str("mpg")
library(dplyr)
glimpse(mpg)
```






#to get the mpg dataset, load the ggplot package first data(mpg)
#as.data.frame(data(mpg)) #converting from list to data frame
```{r}

ggplot(mpg, aes(cty, hwy))+geom_point()
```
1. How many columns are in mpg dataset? 
How about the number of rows? Show thecodes and its result.
```{r}
ncol(mpg)
```
```{r}
nrow(mpg)
```
2. Which manufacturer has the most models in this 
data set? Which model has the most variations? Ans:
```{r, numb2a}
datampg <- mpg
num2a <- datampg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
num2a
colnames(num2a) <- c("Manufacturer", "Model","Counts")
num2a
```
the most models in data sets is dodge which consists of 37 variations


a. Group the manufacturers and find the unique models. Copy the codes and result
```{r}
datampg <- mpg
a <- datampg %>% group_by(manufacturer, model) %>% distinct() %>% count()
a
```
b. Graph the result by using plot() and ggplot(). Write the codes and its result.
plot
```{r}
qplot(model, data = mpg,geom = "bar", fill=manufacturer)
```
ggplot
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

3. Same dataset will be used. You are going to show the relationship of the modelandthe manufacturer.
```{r}
datampg <- mpg
b <- datampg %>% group_by(manufacturer, model) %>% distinct() %>% count()
b
colnames(b) <- c("Manufacturer", "Model")
b
```
a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

b.For you, is it useful? If not, how could you
modify the data to make it more informative?

Yes, it is useful because you can track down the data for each model of the manufacturer and modify it.

. Using the pipe (%>%), group the model and get the number of cars per model. 
Show codes and its result.
```{r}
e <- num2a %>% group_by(Model) %>% count()
e
colnames(e) <- c("Model","Counts")
```

a. Plot using the geom_bar() + coord_flip() just like what is shown below. 
Show codes and its result
```{r}
qplot(model,
      data = mpg,main = "Number of Cars per Model", 
      xlab = "Model",
      ylab = "Number of Cars", 
      geom = "bar", fill = manufacturer) 
 coord_flip()
```
b. Use only the top 20 observations. Show code and results.
```{r}
head(mpg, n=20)
```

5. Plot the relationship between cyl - number of cylinders
and displ - engine displacement using geom_point with aesthetic
colour = engine displacement. Title should be
#“Relationship between No. of Cylinders and Engine Displacement
```{r}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, 
main = "Relationship between No of Cylinders and Engine Displacement")) + 
geom_point(mapping=aes(colour = "engine displacement")) + geom_jitter()
```

b. How would you describe its relationship?
The relationship between data is makking cyl, and y jittered, and the pink 
color indicates engine displacement.

6.Get the total number of observations for drv - type of drive train 
(f = front-wheel drive, r = rear wheel drive, 4 = 4wd) and class -
type of class (Example: suv, 2seater, etc.) 
Plot using the geom_tile() where the number
of observations for class be used as a  fill for aesthetics.
a. Show the codes and its result for the narrative in #6.
```{r}
 ggplot(data = mpg, mapping = aes(x = drv, y = class)) + 
    geom_point(mapping=aes(color=class)) +
   geom_tile()
```

 b. Interpret the result: 
The mapping geometric point graph is used to 
"map" the areas that are covered in black. x as drv and y as class.
 
7. Discuss the difference between these codes. Its outputs 
for each are shown below.

#Code1
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```
 #Code2
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```
8. Try to run the command ?mpg. What is the result of this command?
```{r}
?mpg
```
The result of this command mpg it shows the company
data from 1999 to 2008 for  #38 models of cars.

a. Which variables from mpg dataset are categorical?
The data set are categorized according to their manufacturers name, model
name,engine displacement, in litres, year of manufacture, number of cylinders
Type of transmission, he type of drive train, where f = front-wheel drive, 
r = rear wheel drive, 4 = 4wd, city miles per gallon, highway miles per gallon
highway miles per gallon, and type of car.

b. Which are continuous variables?
Continuous varibles in R was also known as doubles or integers. 

c. Plot the relationship between displ (engine displacement)
and hwy (highway miles per gallon). 
Mapped it with a continuous variable you have identified in #5-b.
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```

What is its result? Why it produced such output? 
The ata tracks the cty by placing cty(city miles per gallon) at color having a 
variation or hues of blue.

9.Plot the relationship between displ (engine displacement)
and hwy(highway miles per gallon) using geom_point(). Add a trend line over 
the existing plot using geom_smooth() with se = FALSE. 
Default method is “loess”.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE, method = loess)
```
10.Using the relationship of displ and hwy, add a trend line over
existing plot. Set the se = FALSE to remove the confidence interval
and method = lm to check for linear modeling
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)
```