---
title: "Individual Project 1"
author: "Mike Anthony Taltal"
date: "2022-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library("twitteR") 
library(dplyr)
library(tidyr)
library("plotly")
library(ggplot2)
library(RColorBrewer)
library(tidytext)
library(rtweet)
library(tm)
library(slam)
library(wordcloud)
library(wordcloud2)
library(corpus)
```

1.Extract from twitter using your developers credentials.Choose any keyword 
you want.
```{r}
CONSUMER_SECRET <- "5fikcIfYieq3Yqaqf80fLRJLITCg10eRSXgUBHkhZa836WnP35"
CONSUMER_KEY <- "mOxonIhWeeb3aT8uKahOJESZB"
ACCESS_SECRET <- "ZAfXCkfu9PFoneXvhWPGaBrn4VwNcsV9Q5pHhGdyrTF9N"
ACCESS_TOKEN <- "1595030186000470017-QRGI98lJnYgTt56G5yqMrrdSmHSMxU"


setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```


2.Get 10000 observations "excluding retweets".
```{r}
tweethere <- searchTwitter("BLACKPINK -filter:retweets",
                           n = 10000,
                           lang = "en",
                           since = "2022-11-19",
                           until = "2022-11-30",
                           retryOnRateLimit= 120) 

```
from list to data frame conversion
```{r}
TWEETIT <- twListToDF(tweethere)
TWEETIT
View(TWEETIT)


save("TWEETIT", file = "TWEETIT.Rdata")
load("TWEETIT.Rdata")

```

3.Plot the time series from the date created. with legends. 
```{r}
ggplot(data = TWEETIT, aes(x = created)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("The Time Series of Blackpink") + 
  scale_fill_gradient(low = "midnightblue", high = "aquamarine4")
```

4.lot a graph (any graph you want)  based on the type of device_
found in Source - that the user use. Include the legends.
```{r}
encodeSource <- function(x) {
  if(grepl(">Twitter for iPhone</a>", x)){
    "Iphone"
  }else if(grepl(">Twitter for iPad</a>", x)){
    "Ipad"
  }else if(grepl(">Twitter for Android</a>", x)){
    "Android"
  } else if(grepl(">Twitter Web Client</a>", x)){
    "Web"
  } else if(grepl(">Twitter for Windows Phone</a>", x)){
    "Windows phone"
  }else if(grepl(">dlvr.it</a>", x)){
    "dlvr.it"
  }else if(grepl(">IFTTT</a>", x)){
    "ifttt"
  }else if(grepl(">Facebook</a>", x)){  #This looks unreliable...
    "Facebook"
  }else {
    "Others"
  }
}

```
```{r}
TWEETIT$tweetSource = sapply (TWEETIT$statusSource, 
                              encodeSource)
tweet_appSource <- TWEETIT %>% 
  select(tweetSource) %>%
  group_by(tweetSource) %>%
  summarize(count=n()) %>%
  arrange(desc(count)) 
Source_subset <- subset(tweet_appSource,count >10)

dataDF <- data.frame(
  category = tweet_appSource$tweetSource,
  count = tweet_appSource$count
)
dataDF$fraction = dataDF$count / sum(dataDF$count)
dataDF$percentage = dataDF$count / sum(dataDF$count) * 100
dataDF$ymax = cumsum(dataDF$fraction)
dataDF$ymin = c(0, head(dataDF$ymax, n=-1))
dataDF$roundP = round(dataDF$percentage, digits = 2)
```
```{r}
ggplot(dataDF,aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, 
                  fill=category)) +
  geom_rect() +
  coord_polar(theta="y") + 
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "right")
```

5. Create a word cloud from the screenName
```{r}
tweet_appScreen <- TWEETIT %>%
  select(screenName) %>%
  group_by(screenName) %>%
  summarize(count=n()) %>%
  arrange(desc(count)) 
```

convert to Corpus
```{r}
namesCorpus <- Corpus(VectorSource(TWEETIT$screenName))
```
Running the code using the wordcloud()
```{r}
wordcloud2(data=tweet_appScreen, 
           size=0.8, 
           color='random-light',
           shape = 'pentagon')
```